Illustrating Good Practice in {\LaTeX}

### 2022-03-27 articles/good_practice.tex
minor changes
I have been meaning to do this for a long time

@@

\begin{theorem}[Bolzano-Weierstrass]
Every bounded sequence has a convergent subsequence.
\end{theorem}

@@

\begin{lemma}
Cauchy sequences are bounded.
\end{lemma}

>>>>

% No auto-indent
\setlength{\parindent}{0pt}

@@

\begin{mdframed}[backgroundcolor=black!4, align=center, userdefinedwidth=40em, topline=false, bottomline = false, leftline = false, rightline = false, frametitle = {Bolzano-Weierstrass Theorem}]
Every bounded sequence has a convergent subsequence.
\end{mdframed}

@@

\begin{mdframed}[backgroundcolor=black!4, align=center, userdefinedwidth=40em, topline=false, bottomline = false, leftline = false, rightline = false, frametitle = {Lemma}]
Cauchy sequences are bounded.
\end{mdframed}
